---
title: "the shire"
output: html_document
---
this file creates the 1% variance trees as well as writing them to a csv file that can be submitted to the kaggel challenge. This document works similar to the fangorn rmd file in the way that it optimizes random forest structure. level has a clean names filter applied to it to fix any lingering naming issues that may be present.  the variant file has a drug column applied to it one at a time so the first set is drug one and so on. This set is then run an initial time to get a baseline with the default settings of the randomforest() function including a split per tree of 3 and 500 trees. First the trees are optimized by seeing the error rate per tree and the overall out of bag rate for each model the graphing allows the user to see where the trees begin to level out. The user then manually adjusts the number of trees in the model until the graph shows a leveling out in the 3 categories.  Once this step is complete using the new tree count a loop is run where each model is created 20 times with varying splits from 1-20. From this the error rates for each model is displayed and the one with the lowest is chosen as the split number for the model. This new split number and tree number are then fed back into the randomforest() function and the final model is created for that drug/variance level combination. Then the predict function is run on each of the drug models and out puts a probability matrix for each of the drug cell line combinations this is saved under its drug cell line combination to a csv file named submission that is written out and used to submit to kaggel. 

Note as above the code can get confusing  a key is below:

Shirex= is the completed modle where x is the drug used in it

Treex= the one percent variance table fed to the random forest model that is a concatenation of both the test set and the drug for that section

```{r}
sessionInfo()
```

```{r}
set.seed(25000)
library(tidyverse)
library(ggplot2)
library(cowplot)
library(randomForest)
library(parallel)
library(skimr)
library(broom)
library(janitor)
library(dplyr)
library(readr)
library(genefilter)

```

```{r import}
# Read in the cleaned expression data
expression <- as.data.frame((read.table("../data/clean_expression.txt", row.names=1 )))
rownames(expression)[1] <- '184A1'# Rename the only integer name

# Read in the subtype data
subtypes <- read_tsv("../data/clean_subtypes.txt")

# Read in the truth set
truth_set <-  as.data.frame((read.table("../data/clean_training_answers.txt", row.names=1 )))


# Create merged feature set
featureSet<-cbind(subtypes[,2],t(expression))

#read in the submission table
submission<-as.data.frame((read.csv("../data/scoring_and_test_set_id_mappings.csv")))
submission[ , 'train_accuracy'] <- NA

#read in the test sethead
test<-as.data.frame(t(read.table("../data/clean_test_expression.txt", row.names=1 )))
test<-clean_names(test)
```
#variance 
```{r}
#overview of variance 
expVar <- (rowVars(expression))
hist(expVar)
expVar <- as.data.frame(expVar)
names(expVar) <- c('variance')

paste('max variance:', max(expVar[,1]))
paste('min variance:', min(expVar[,1]))

#top 1 of genes
expVar %>% count((variance > '3.5'))
top <- expVar$variance > 3.5
root <- expression[top,]
root<-data.frame(t(root))
dim(root)
```

#drug 1
```{r}
#attaching the first drug to the test set
tree1<-cbind(drug=truth_set[,1],root)
tree1<-clean_names(tree1)
tree1$drug<-factor(tree1$drug)

```

```{r}
#creation of the foret
set.seed(1)
shire <- randomForest( drug∼.,data=tree1  ,mtry=3,ntree=1000)
shire
```

```{r}
#optimization of the trees
set.seed(1)
oob.error.shire <- data.frame(
  Trees=rep(1:nrow(shire$err.rate), times=3),
  Type=rep(c("OOB", "1", "0"), each=nrow(shire$err.rate)),
  Error=c(shire$err.rate[,"OOB"],
    shire$err.rate[,"1"],
    shire$err.rate[,"0"]))

ggplot(data=oob.error.shire, aes(x=Trees, y=Error)) +
  geom_line(aes(color=Type))+ggtitle("forest of 1% variance")
```

```{r}
#optimization of splits
set.seed(1)
#split optimization
oob.values <- vector(length=20)
for(i in 1:20) {
  temp.model <- randomForest(drug ~ ., data=tree1, mtry=i, ntree=1000)
  oob.values[i] <- temp.model$err.rate[nrow(temp.model$err.rate),1]
}
oob.values

```

```{r}
#final model 
#assumes 0.48 nis the lowest 
set.seed(1)
shire <- randomForest( drug∼.,data=tree1  ,mtry=2,ntree=1000)
shire
```



#drug 2
```{r}
#attaching the second drug to the test set
tree2<-cbind(drug=truth_set[,2],root)
tree2<-clean_names(tree2)
tree2$drug<-factor(tree2$drug)

```

```{r}
#creation of primary forest
set.seed(1)
shire2 <- randomForest( drug∼.,data=tree2  ,mtry=3,ntree=500)
shire2
```

```{r}
#optimization of trees
set.seed(1)
oob.error.shire2 <- data.frame(
  Trees=rep(1:nrow(shire2$err.rate), times=3),
  Type=rep(c("OOB", "1", "0"), each=nrow(shire2$err.rate)),
  Error=c(shire2$err.rate[,"OOB"],
    shire2$err.rate[,"1"],
    shire2$err.rate[,"0"]))

ggplot(data=oob.error.shire2, aes(x=Trees, y=Error)) +
  geom_line(aes(color=Type))+ggtitle("forest of 1% variance")
```

```{r}
set.seed(1)
#split optimization
oob.values <- vector(length=20)
for(i in 1:20) {
  temp.model <- randomForest(drug ~ ., data=tree2, mtry=i, ntree=500)
  oob.values[i] <- temp.model$err.rate[nrow(temp.model$err.rate),1]
}
oob.values

```

```{r}
#final model
#assumes 0.20 nis the lowest 
set.seed(1)
shire2 <- randomForest( drug∼.,data=tree2  ,mtry=2,ntree=500)
shire2
```

#drug 3
```{r}
#attaching drug 3 to the test set
tree3<-cbind(drug=truth_set[,3],root)
tree3<-clean_names(tree3)
tree3$drug<-factor(tree3$drug)

```

```{r}
#primary model
set.seed(1)
shire3 <- randomForest( drug∼.,data=tree3  ,mtry=3,ntree=500)
shire3
```

```{r}
#optimization of trees
set.seed(1)
oob.error.shire3 <- data.frame(
  Trees=rep(1:nrow(shire3$err.rate), times=3),
  Type=rep(c("OOB", "1", "0"), each=nrow(shire3$err.rate)),
  Error=c(shire3$err.rate[,"OOB"],
    shire3$err.rate[,"1"],
    shire3$err.rate[,"0"]))

ggplot(data=oob.error.shire3, aes(x=Trees, y=Error)) +
  geom_line(aes(color=Type))+ggtitle("forest of 1% variance")
```

```{r}
set.seed(1)
#split optimization
oob.values <- vector(length=20)
for(i in 1:20) {
  temp.model <- randomForest(drug ~ ., data=tree3, mtry=i, ntree=500)
  oob.values[i] <- temp.model$err.rate[nrow(temp.model$err.rate),1]
}
oob.values

```

```{r}
#final model
#assumes 0.20 nis the lowest 
set.seed(1)
shire3 <- randomForest( drug∼.,data=tree3  ,mtry=9,ntree=500)
shire3
```
#drug4
```{r}
#attaching the 4th drug to the data set
tree4<-cbind(drug=truth_set[,4],root)
tree4<-clean_names(tree4)
tree4$drug<-factor(tree4$drug)

```

```{r}
#primary model
set.seed(1)
shire4 <- randomForest( drug∼.,data=tree4  ,mtry=3,ntree=500)
shire4
```

```{r}
#optimising trees
set.seed(1)
oob.error.shire4 <- data.frame(
  Trees=rep(1:nrow(shire4$err.rate), times=3),
  Type=rep(c("OOB", "1", "0"), each=nrow(shire4$err.rate)),
  Error=c(shire4$err.rate[,"OOB"],
    shire4$err.rate[,"1"],
    shire4$err.rate[,"0"]))

ggplot(data=oob.error.shire4, aes(x=Trees, y=Error)) +
  geom_line(aes(color=Type))+ggtitle("forest of 1% variance")
```

```{r}
set.seed(1)
#split optimization
oob.values <- vector(length=20)
for(i in 1:20) {
  temp.model <- randomForest(drug ~ ., data=tree4, mtry=i, ntree=500)
  oob.values[i] <- temp.model$err.rate[nrow(temp.model$err.rate),1]
}
oob.values

```

```{r}
#final model
#assumes 0.32 nis the lowest 
set.seed(1)
shire2 <- randomForest( drug∼.,data=tree4  ,mtry=10,ntree=500)
shire2
```

#drug5
```{r}
#attaching the fith drug to the data set
tree5<-cbind(drug=truth_set[,5],root)
tree5<-clean_names(tree5)
tree5$drug<-factor(tree5$drug)

```

```{r}
#primary model 
set.seed(1)
shire5 <- randomForest( drug∼.,data=tree5  ,mtry=3,ntree=1000)
shire5
```

```{r}
#optimising trees
set.seed(1)
oob.error.shire5 <- data.frame(
  Trees=rep(1:nrow(shire5$err.rate), times=3),
  Type=rep(c("OOB", "1", "0"), each=nrow(shire5$err.rate)),
  Error=c(shire5$err.rate[,"OOB"],
    shire5$err.rate[,"1"],
    shire5$err.rate[,"0"]))

ggplot(data=oob.error.shire5, aes(x=Trees, y=Error)) +
  geom_line(aes(color=Type))+ggtitle("forest of 1% variance")
```

```{r}
set.seed(1)
#split optimization
oob.values <- vector(length=20)
for(i in 1:20) {
  temp.model <- randomForest(drug ~ ., data=tree5, mtry=i, ntree=1000)
  oob.values[i] <- temp.model$err.rate[nrow(temp.model$err.rate),1]
}
oob.values

```

```{r}
#final model
#assumes 0.32 nis the lowest 
set.seed(1)
shire5 <- randomForest( drug∼.,data=tree5  ,mtry=5,ntree=1000)
shire5
```
#drug6
```{r}
#attaching drug 6 to the data set
tree6<-cbind(drug=truth_set[,6],root)
tree6<-clean_names(tree6)
tree6$drug<-factor(tree6$drug)

```

```{r}
#priomary model
set.seed(1)
shire6 <- randomForest( drug∼.,data=tree6  ,mtry=3,ntree=500)
shire6
```

```{r}
##optimization of trees
set.seed(1)
oob.error.shire6 <- data.frame(
  Trees=rep(1:nrow(shire6$err.rate), times=3),
  Type=rep(c("OOB", "1", "0"), each=nrow(shire6$err.rate)),
  Error=c(shire6$err.rate[,"OOB"],
    shire6$err.rate[,"1"],
    shire6$err.rate[,"0"]))

ggplot(data=oob.error.shire6, aes(x=Trees, y=Error)) +
  geom_line(aes(color=Type))+ggtitle("forest of 1% variance")
```

```{r}
set.seed(1)
#split optimization
oob.values <- vector(length=20)
for(i in 1:20) {
  temp.model <- randomForest(drug ~ ., data=tree6, mtry=i, ntree=500)
  oob.values[i] <- temp.model$err.rate[nrow(temp.model$err.rate),1]
}
oob.values

```

```{r}
#final model
#assumes 0.32 nis the lowest 
set.seed(1)
shire6 <- randomForest( drug∼.,data=tree6  ,mtry=5,ntree=1000)
shire6
```
#drug 7
```{r}
#attaching drug 7 to the data set
tree7<-cbind(drug=truth_set[,7],root)
tree7<-clean_names(tree7)
tree7$drug<-factor(tree7$drug)

```

```{r}
#primary model
set.seed(1)
shire7 <- randomForest( drug∼.,data=tree7  ,mtry=3,ntree=3000)
shire7
```

```{r}
#optimization of trees
set.seed(1)
oob.error.shire7 <- data.frame(
  Trees=rep(1:nrow(shire7$err.rate), times=3),
  Type=rep(c("OOB", "1", "0"), each=nrow(shire7$err.rate)),
  Error=c(shire7$err.rate[,"OOB"],
    shire7$err.rate[,"1"],
    shire7$err.rate[,"0"]))

ggplot(data=oob.error.shire7, aes(x=Trees, y=Error)) +
  geom_line(aes(color=Type))+ggtitle("forest of 1% variance")
```

```{r}
set.seed(1)
#split optimization
oob.values <- vector(length=20)
for(i in 1:20) {
  temp.model <- randomForest(drug ~ ., data=tree7, mtry=i, ntree=3000)
  oob.values[i] <- temp.model$err.rate[nrow(temp.model$err.rate),1]
}
oob.values

```

```{r}
#final model
#assumes 0.32 nis the lowest 
set.seed(1)
shire7 <- randomForest( drug∼.,data=tree7  ,mtry=6,ntree=3000)
shire7
```
#drug 8
```{r}
#attaching drug 8 to the data set
tree8<-cbind(drug=truth_set[,8],root)
tree8<-clean_names(tree8)
tree8$drug<-factor(tree8$drug)

```

```{r}
#primary model
set.seed(1)
shire8 <- randomForest( drug∼.,data=tree8  ,mtry=3,ntree=1000)
shire8
```

```{r}
#optimization of trees
set.seed(1)
oob.error.shire8 <- data.frame(
  Trees=rep(1:nrow(shire8$err.rate), times=3),
  Type=rep(c("OOB", "1", "0"), each=nrow(shire8$err.rate)),
  Error=c(shire8$err.rate[,"OOB"],
    shire8$err.rate[,"1"],
    shire8$err.rate[,"0"]))

ggplot(data=oob.error.shire8, aes(x=Trees, y=Error)) +
  geom_line(aes(color=Type))+ggtitle("forest of 1% variance")
```

```{r}
set.seed(1)
#split optimization
oob.values <- vector(length=20)
for(i in 1:20) {
  temp.model <- randomForest(drug ~ ., data=tree8, mtry=i, ntree=1000)
  oob.values[i] <- temp.model$err.rate[nrow(temp.model$err.rate),1]
}
oob.values

```

```{r}
#final model
#assumes 0.24 nis the lowest 
set.seed(1)
shire8 <- randomForest( drug∼.,data=tree8  ,mtry=3,ntree=1000)
shire8
```
#drug 9
```{r}
#attaching drug 9 to the data set
tree9<-cbind(drug=truth_set[,9],root)
tree9<-clean_names(tree9)
tree9$drug<-factor(tree9$drug)

```

```{r}
#primary model
set.seed(1)
shire9 <- randomForest( drug∼.,data=tree9  ,mtry=3,ntree=1000)
shire9
```

```{r}
#optimising trees
set.seed(1)
oob.error.shire9 <- data.frame(
  Trees=rep(1:nrow(shire9$err.rate), times=3),
  Type=rep(c("OOB", "1", "0"), each=nrow(shire9$err.rate)),
  Error=c(shire9$err.rate[,"OOB"],
    shire9$err.rate[,"1"],
    shire9$err.rate[,"0"]))

ggplot(data=oob.error.shire9, aes(x=Trees, y=Error)) +
  geom_line(aes(color=Type))+ggtitle("forest of 1% variance")
```

```{r}
set.seed(1)
#split optimization
oob.values <- vector(length=20)
for(i in 1:20) {
  temp.model <- randomForest(drug ~ ., data=tree9, mtry=i, ntree=1000)
  oob.values[i] <- temp.model$err.rate[nrow(temp.model$err.rate),1]
}
oob.values

```

```{r}
#final model
#assumes 0.32 nis the lowest 
set.seed(1)
shire9 <- randomForest( drug∼.,data=tree9  ,mtry=3,ntree=1000)
shire9
```
#drug 10
```{r}
#attaching drug 10 to the data set 
tree10<-cbind(drug=truth_set[,10],root)
tree10<-clean_names(tree10)
tree10$drug<-factor(tree10$drug)

```

```{r}
#primary model
set.seed(1)
shire10 <- randomForest( drug∼.,data=tree10  ,mtry=3,ntree=1500)
shire10
```

```{r}
#optimising trees
set.seed(1)
oob.error.shire10 <- data.frame(
  Trees=rep(1:nrow(shire10$err.rate), times=3),
  Type=rep(c("OOB", "1", "0"), each=nrow(shire10$err.rate)),
  Error=c(shire10$err.rate[,"OOB"],
    shire10$err.rate[,"1"],
    shire10$err.rate[,"0"]))

ggplot(data=oob.error.shire10, aes(x=Trees, y=Error)) +
  geom_line(aes(color=Type))+ggtitle("forest of 1% variance")
```

```{r}
set.seed(1)
#split optimization
oob.values <- vector(length=20)
for(i in 1:20) {
  temp.model <- randomForest(drug ~ ., data=tree10, mtry=i, ntree=1500)
  oob.values[i] <- temp.model$err.rate[nrow(temp.model$err.rate),1]
}
oob.values

```

```{r}
#final Model
#assumes 0.32 nis the lowest 
set.seed(1)
shire10 <- randomForest( drug∼.,data=tree10  ,mtry=3,ntree=1500)
shire10
```
#drug11
```{r}
#attaching drug 11 to the data set
tree11<-cbind(drug=truth_set[,11],root)
tree11<-clean_names(tree11)
tree11$drug<-factor(tree11$drug)

```

```{r}
#primary model
set.seed(1)
shire11<- randomForest( drug∼.,data=tree11  ,mtry=3,ntree=1000)
shire11
```

```{r}
#tree optimization
set.seed(1)
oob.error.shire11 <- data.frame(
  Trees=rep(1:nrow(shire11$err.rate), times=3),
  Type=rep(c("OOB", "1", "0"), each=nrow(shire11$err.rate)),
  Error=c(shire11$err.rate[,"OOB"],
    shire11$err.rate[,"1"],
    shire11$err.rate[,"0"]))

ggplot(data=oob.error.shire11, aes(x=Trees, y=Error)) +
  geom_line(aes(color=Type))+ggtitle("forest of 1% variance")
```

```{r}
set.seed(1)
#split optimization
oob.values <- vector(length=20)
for(i in 1:20) {
  temp.model <- randomForest(drug ~ ., data=tree11, mtry=i, ntree=1000)
  oob.values[i] <- temp.model$err.rate[nrow(temp.model$err.rate),1]
}
oob.values

```

```{r}
#final model
#assumes 0.32 nis the lowest 
set.seed(1)
shire11 <- randomForest( drug∼.,data=tree11  ,mtry=3,ntree=1000)
shire11
```

#drug 12
```{r}
#attaching drug 12 to the test set
tree12<-cbind(drug=truth_set[,12],root)
tree12<-clean_names(tree12)
tree12$drug<-factor(tree12$drug)

```

```{r}
##primary model
set.seed(1)
shire12<- randomForest( drug∼.,data=tree12  ,mtry=3,ntree=1500)
shire12
```

```{r}
#tree optimization
set.seed(1)
oob.error.shire12 <- data.frame(
  Trees=rep(1:nrow(shire12$err.rate), times=3),
  Type=rep(c("OOB", "1", "0"), each=nrow(shire12$err.rate)),
  Error=c(shire12$err.rate[,"OOB"],
    shire12$err.rate[,"1"],
    shire12$err.rate[,"0"]))

ggplot(data=oob.error.shire12, aes(x=Trees, y=Error)) +
  geom_line(aes(color=Type))+ggtitle("forest of 1% variance")
```

```{r}
set.seed(1)
#split optimization
oob.values <- vector(length=20)
for(i in 1:20) {
  temp.model <- randomForest(drug ~ ., data=tree12, mtry=i, ntree=1500)
  oob.values[i] <- temp.model$err.rate[nrow(temp.model$err.rate),1]
}
oob.values

```

```{r}
#final model
#assumes 0.32 nis the lowest 
set.seed(1)
shire11 <- randomForest( drug∼.,data=tree11  ,mtry=3,ntree=1500)
shire11
```

#this is the section for the test set 

```{r}
#variance filtering of top 1%
top <- expVar$variance > 3.5 
test<- test[,(top)]
test<-clean_names(test)
colnames(test)[1]<-"x184a1"
```
#drug1
```{r}
#running of selected model
pred.of = predict(shire,test,type='prob')

#write into the submission file

ind <- which((submission[,1]=="HCC1187" & submission[,2]=="CGC-11047"))
submission[ind, 5] <- pred.of[4,2]

ind <- which((submission[,1]=="MCF7" & submission[,2]=="CGC-11047"))
submission[ind, 5] <- pred.of[10,2]

ind <- which((submission[,1]=="MDAMB361" & submission[,2]=="CGC-11047"))
submission[ind, 5] <- pred.of[13,2]

ind <- which((submission[,1]=="MDAMB231" & submission[,2]=="CGC-11047"))
submission[ind, 5] <- pred.of[12,2]

ind <- which((submission[,1]=="BT549" & submission[,2]=="CGC-11047"))
submission[ind, 5] <- pred.of[3,2]

ind <- which((submission[,1]=="600MPE" & submission[,2]=="CGC-11047"))
submission[ind, 5] <- pred.of[1,2]

ind <- which((submission[,1]=="HCC1954" & submission[,2]=="CGC-11047"))
submission[ind, 5] <- pred.of[5,2]

ind <- which((submission[,1]=="SKBR3" & submission[,2]=="CGC-11047"))
submission[ind, 5] <- pred.of[14,2]

ind <- which((submission[,1]=="MCF12A" & submission[,2]=="CGC-11047"))
submission[ind, 5] <- pred.of[9,2]

ind <- which((submission[,1]=="HCC3153" & submission[,2]=="CGC-11047"))
submission[ind, 5] <- pred.of[6,2]

ind <- which((submission[,1]=="MDAMB157" & submission[,2]=="CGC-11047"))
submission[ind, 5] <- pred.of[11,2]

ind <- which((submission[,1]=="LY2" & submission[,2]=="CGC-11047"))
submission[ind, 5] <- pred.of[7,2]

ind <- which((submission[,1]=="AU565" & submission[,2]=="CGC-11047"))
submission[ind, 5] <- pred.of[2,2]

ind <- which((submission[,1]=="MCF10A" & submission[,2]=="CGC-11047"))
submission[ind, 5] <- pred.of[8,2]

```


#drug2
```{r}
#running of selected model
pred.of = predict(shire2,test,type='prob')


#write into the submission file

ind <- which((submission[,1]=="HCC1187" & submission[,2]=="Carboplatin"))
submission[ind, 5] <- pred.of[4,2]

ind <- which((submission[,1]=="MCF7" & submission[,2]=="Carboplatin"))
submission[ind, 5] <- pred.of[10,2]

ind <- which((submission[,1]=="MDAMB361" & submission[,2]=="Carboplatin"))
submission[ind, 5] <- pred.of[13,2]

ind <- which((submission[,1]=="MDAMB231" & submission[,2]=="Carboplatin"))
submission[ind, 5] <- pred.of[12,2]

ind <- which((submission[,1]=="BT549" & submission[,2]=="Carboplatin"))
submission[ind, 5] <- pred.of[3,2]

ind <- which((submission[,1]=="600MPE" & submission[,2]=="Carboplatin"))
submission[ind, 5] <- pred.of[1,2]

ind <- which((submission[,1]=="HCC1954" & submission[,2]=="Carboplatin"))
submission[ind, 5] <- pred.of[5,2]

ind <- which((submission[,1]=="SKBR3" & submission[,2]=="Carboplatin"))
submission[ind, 5] <- pred.of[14,2]

ind <- which((submission[,1]=="MCF12A" & submission[,2]=="Carboplatin"))
submission[ind, 5] <- pred.of[9,2]

ind <- which((submission[,1]=="HCC3153" & submission[,2]=="Carboplatin"))
submission[ind, 5] <- pred.of[6,2]

ind <- which((submission[,1]=="MDAMB157" & submission[,2]=="Carboplatin"))
submission[ind, 5] <- pred.of[11,2]

ind <- which((submission[,1]=="LY2" & submission[,2]=="Carboplatin"))
submission[ind, 5] <- pred.of[7,2]

ind <- which((submission[,1]=="AU565" & submission[,2]=="Carboplatin"))
submission[ind, 5] <- pred.of[2,2]

ind <- which((submission[,1]=="MCF10A" & submission[,2]=="Carboplatin"))
submission[ind, 5] <- pred.of[8,2]
```


#drug3
```{r}
#running of selected model
pred.of = predict(shire3,test,type='prob')

#write into the submission file

ind <- which((submission[,1]=="HCC1187" & submission[,2]=="Cisplatin"))
submission[ind, 5] <- pred.of[4,2]

ind <- which((submission[,1]=="MCF7" & submission[,2]=="Cisplatin"))
submission[ind, 5] <- pred.of[10,2]

ind <- which((submission[,1]=="MDAMB361" & submission[,2]=="Cisplatin"))
submission[ind, 5] <- pred.of[13,2]

ind <- which((submission[,1]=="MDAMB231" & submission[,2]=="Cisplatin"))
submission[ind, 5] <- pred.of[12,2]

ind <- which((submission[,1]=="BT549" & submission[,2]=="Cisplatin"))
submission[ind, 5] <- pred.of[3,2]

ind <- which((submission[,1]=="600MPE" & submission[,2]=="Cisplatin"))
submission[ind, 5] <- pred.of[1,2]

ind <- which((submission[,1]=="HCC1954" & submission[,2]=="Cisplatin"))
submission[ind, 5] <- pred.of[5,2]

ind <- which((submission[,1]=="SKBR3" & submission[,2]=="Cisplatin"))
submission[ind, 5] <- pred.of[14,2]

ind <- which((submission[,1]=="MCF12A" & submission[,2]=="Cisplatin"))
submission[ind, 5] <- pred.of[9,2]

ind <- which((submission[,1]=="HCC3153" & submission[,2]=="Cisplatin"))
submission[ind, 5] <- pred.of[6,2]

ind <- which((submission[,1]=="MDAMB157" & submission[,2]=="Cisplatin"))
submission[ind, 5] <- pred.of[11,2]

ind <- which((submission[,1]=="LY2" & submission[,2]=="Cisplatin"))
submission[ind, 5] <- pred.of[7,2]

ind <- which((submission[,1]=="AU565" & submission[,2]=="Cisplatin"))
submission[ind, 5] <- pred.of[2,2]

ind <- which((submission[,1]=="MCF10A" & submission[,2]=="Cisplatin"))
submission[ind, 5] <- pred.of[8,2]
```


#drug4
```{r}
#running of selected model
pred.of = predict(shire4,test,type='prob')

#write into the submission file

ind <- which((submission[,1]=="HCC1187" & submission[,2]=="GSK1070916"))
submission[ind, 5] <- pred.of[4,2]

ind <- which((submission[,1]=="MCF7" & submission[,2]=="GSK1070916"))
submission[ind, 5] <- pred.of[10,2]

ind <- which((submission[,1]=="MDAMB361" & submission[,2]=="GSK1070916"))
submission[ind, 5] <- pred.of[13,2]

ind <- which((submission[,1]=="MDAMB231" & submission[,2]=="GSK1070916"))
submission[ind, 5] <- pred.of[12,2]

ind <- which((submission[,1]=="BT549" & submission[,2]=="GSK1070916"))
submission[ind, 5] <- pred.of[3,2]

ind <- which((submission[,1]=="600MPE" & submission[,2]=="GSK1070916"))
submission[ind, 5] <- pred.of[1,2]

ind <- which((submission[,1]=="HCC1954" & submission[,2]=="GSK1070916"))
submission[ind, 5] <- pred.of[5,2]

ind <- which((submission[,1]=="SKBR3" & submission[,2]=="GSK1070916"))
submission[ind, 5] <- pred.of[14,2]

ind <- which((submission[,1]=="MCF12A" & submission[,2]=="GSK1070916"))
submission[ind, 5] <- pred.of[9,2]

ind <- which((submission[,1]=="HCC3153" & submission[,2]=="GSK1070916"))
submission[ind, 5] <- pred.of[6,2]

ind <- which((submission[,1]=="MDAMB157" & submission[,2]=="GSK1070916"))
submission[ind, 5] <- pred.of[11,2]

ind <- which((submission[,1]=="LY2" & submission[,2]=="GSK1070916"))
submission[ind, 5] <- pred.of[7,2]

ind <- which((submission[,1]=="AU565" & submission[,2]=="GSK1070916"))
submission[ind, 5] <- pred.of[2,2]

ind <- which((submission[,1]=="MCF10A" & submission[,2]=="GSK1070916"))
submission[ind, 5] <- pred.of[8,2]
```


#drug5
```{r}
#running of selected model
pred.of = predict(shire5,test,type='prob')

#write into the submission file

ind <- which((submission[,1]=="HCC1187" & submission[,2]=="GSK1120212"))
submission[ind, 5] <- pred.of[4,2]

ind <- which((submission[,1]=="MCF7" & submission[,2]=="GSK1120212"))
submission[ind, 5] <- pred.of[10,2]

ind <- which((submission[,1]=="MDAMB361" & submission[,2]=="GSK1120212"))
submission[ind, 5] <- pred.of[13,2]

ind <- which((submission[,1]=="MDAMB231" & submission[,2]=="GSK1120212"))
submission[ind, 5] <- pred.of[12,2]

ind <- which((submission[,1]=="BT549" & submission[,2]=="GSK1120212"))
submission[ind, 5] <- pred.of[3,2]

ind <- which((submission[,1]=="600MPE" & submission[,2]=="GSK1120212"))
submission[ind, 5] <- pred.of[1,2]

ind <- which((submission[,1]=="HCC1954" & submission[,2]=="GSK1120212"))
submission[ind, 5] <- pred.of[5,2]

ind <- which((submission[,1]=="SKBR3" & submission[,2]=="GSK1120212"))
submission[ind, 5] <- pred.of[14,2]

ind <- which((submission[,1]=="MCF12A" & submission[,2]=="GSK1120212"))
submission[ind, 5] <- pred.of[9,2]

ind <- which((submission[,1]=="HCC3153" & submission[,2]=="GSK1120212"))
submission[ind, 5] <- pred.of[6,2]

ind <- which((submission[,1]=="MDAMB157" & submission[,2]=="GSK1120212"))
submission[ind, 5] <- pred.of[11,2]

ind <- which((submission[,1]=="LY2" & submission[,2]=="GSK1120212"))
submission[ind, 5] <- pred.of[7,2]

ind <- which((submission[,1]=="AU565" & submission[,2]=="GSK1120212"))
submission[ind, 5] <- pred.of[2,2]

ind <- which((submission[,1]=="MCF10A" & submission[,2]=="GSK1120212"))
submission[ind, 5] <- pred.of[8,2]
```


#drug6
```{r}
#running of selected model
pred.of = predict(shire6,test,type='prob')
#writing to file
ind <- which((submission[,1]=="HCC1187" & submission[,2]=="GSK461364"))
submission[ind, 5] <- pred.of[4,2]

ind <- which((submission[,1]=="MCF7" & submission[,2]=="GSK461364"))
submission[ind, 5] <- pred.of[10,2]

ind <- which((submission[,1]=="MDAMB361" & submission[,2]=="GSK461364"))
submission[ind, 5] <- pred.of[13,2]

ind <- which((submission[,1]=="MDAMB231" & submission[,2]=="GSK461364"))
submission[ind, 5] <- pred.of[12,2]

ind <- which((submission[,1]=="BT549" & submission[,2]=="GSK461364"))
submission[ind, 5] <- pred.of[3,2]

ind <- which((submission[,1]=="600MPE" & submission[,2]=="GSK461364"))
submission[ind, 5] <- pred.of[1,2]

ind <- which((submission[,1]=="HCC1954" & submission[,2]=="GSK461364"))
submission[ind, 5] <- pred.of[5,2]

ind <- which((submission[,1]=="SKBR3" & submission[,2]=="GSK461364"))
submission[ind, 5] <- pred.of[14,2]

ind <- which((submission[,1]=="MCF12A" & submission[,2]=="GSK461364"))
submission[ind, 5] <- pred.of[9,2]

ind <- which((submission[,1]=="HCC3153" & submission[,2]=="GSK461364"))
submission[ind, 5] <- pred.of[6,2]

ind <- which((submission[,1]=="MDAMB157" & submission[,2]=="GSK461364"))
submission[ind, 5] <- pred.of[11,2]

ind <- which((submission[,1]=="LY2" & submission[,2]=="GSK461364"))
submission[ind, 5] <- pred.of[7,2]

ind <- which((submission[,1]=="AU565" & submission[,2]=="GSK461364"))
submission[ind, 5] <- pred.of[2,2]

ind <- which((submission[,1]=="MCF10A" & submission[,2]=="GSK461364"))
submission[ind, 5] <- pred.of[8,2]
```


#drug7
```{r}
#running of selected model
pred.of = predict(shire7,test,type='prob')

#write into the submission file

ind <- which((submission[,1]=="HCC1187" & submission[,2]=="Geldanamycin"))
submission[ind, 5] <- pred.of[4,2]

ind <- which((submission[,1]=="MCF7" & submission[,2]=="Geldanamycin"))
submission[ind, 5] <- pred.of[10,2]

ind <- which((submission[,1]=="MDAMB361" & submission[,2]=="Geldanamycin"))
submission[ind, 5] <- pred.of[13,2]

ind <- which((submission[,1]=="MDAMB231" & submission[,2]=="Geldanamycin"))
submission[ind, 5] <- pred.of[12,2]

ind <- which((submission[,1]=="BT549" & submission[,2]=="Geldanamycin"))
submission[ind, 5] <- pred.of[3,2]

ind <- which((submission[,1]=="600MPE" & submission[,2]=="Geldanamycin"))
submission[ind, 5] <- pred.of[1,2]

ind <- which((submission[,1]=="HCC1954" & submission[,2]=="Geldanamycin"))
submission[ind, 5] <- pred.of[5,2]

ind <- which((submission[,1]=="SKBR3" & submission[,2]=="Geldanamycin"))
submission[ind, 5] <- pred.of[14,2]

ind <- which((submission[,1]=="MCF12A" & submission[,2]=="Geldanamycin"))
submission[ind, 5] <- pred.of[9,2]

ind <- which((submission[,1]=="HCC3153" & submission[,2]=="Geldanamycin"))
submission[ind, 5] <- pred.of[6,2]

ind <- which((submission[,1]=="MDAMB157" & submission[,2]=="Geldanamycin"))
submission[ind, 5] <- pred.of[11,2]

ind <- which((submission[,1]=="LY2" & submission[,2]=="Geldanamycin"))
submission[ind, 5] <- pred.of[7,2]

ind <- which((submission[,1]=="AU565" & submission[,2]=="Geldanamycin"))
submission[ind, 5] <- pred.of[2,2]

ind <- which((submission[,1]=="MCF10A" & submission[,2]=="Geldanamycin"))
submission[ind, 5] <- pred.of[8,2]
```


#drug8
```{r}
#running of selected model
pred.of = predict(shire,test,type='prob')


#write into the submission file

ind <- which((submission[,1]=="HCC1187" & submission[,2]=="Oxaliplatin"))
submission[ind, 5] <- pred.of[4,2]

ind <- which((submission[,1]=="MCF7" & submission[,2]=="Oxaliplatin"))
submission[ind, 5] <- pred.of[10,2]

ind <- which((submission[,1]=="MDAMB361" & submission[,2]=="Oxaliplatin"))
submission[ind, 5] <- pred.of[13,2]

ind <- which((submission[,1]=="MDAMB231" & submission[,2]=="Oxaliplatin"))
submission[ind, 5] <- pred.of[12,2]

ind <- which((submission[,1]=="BT549" & submission[,2]=="Oxaliplatin"))
submission[ind, 5] <- pred.of[3,2]

ind <- which((submission[,1]=="600MPE" & submission[,2]=="Oxaliplatin"))
submission[ind, 5] <- pred.of[1,2]

ind <- which((submission[,1]=="HCC1954" & submission[,2]=="Oxaliplatin"))
submission[ind, 5] <- pred.of[5,2]

ind <- which((submission[,1]=="SKBR3" & submission[,2]=="Oxaliplatin"))
submission[ind, 5] <- pred.of[14,2]

ind <- which((submission[,1]=="MCF12A" & submission[,2]=="Oxaliplatin"))
submission[ind, 5] <- pred.of[9,2]

ind <- which((submission[,1]=="HCC3153" & submission[,2]=="Oxaliplatin"))
submission[ind, 5] <- pred.of[6,2]

ind <- which((submission[,1]=="MDAMB157" & submission[,2]=="Oxaliplatin"))
submission[ind, 5] <- pred.of[11,2]

ind <- which((submission[,1]=="LY2" & submission[,2]=="Oxaliplatin"))
submission[ind, 5] <- pred.of[7,2]

ind <- which((submission[,1]=="AU565" & submission[,2]=="Oxaliplatin"))
submission[ind, 5] <- pred.of[2,2]

ind <- which((submission[,1]=="MCF10A" & submission[,2]=="Oxaliplatin"))
submission[ind, 5] <- pred.of[8,2]


```


#drug9
```{r}
#running of selected model
pred.of = predict(shire9,test,type='prob')

#write into the submission file

ind <- which((submission[,1]=="HCC1187" & submission[,2]=="PF-3084014"))
submission[ind, 5] <- pred.of[4,2]

ind <- which((submission[,1]=="MCF7" & submission[,2]=="PF-3084014"))
submission[ind, 5] <- pred.of[10,2]

ind <- which((submission[,1]=="MDAMB361" & submission[,2]=="PF-3084014"))
submission[ind, 5] <- pred.of[13,2]

ind <- which((submission[,1]=="MDAMB231" & submission[,2]=="PF-3084014"))
submission[ind, 5] <- pred.of[12,2]

ind <- which((submission[,1]=="BT549" & submission[,2]=="PF-3084014"))
submission[ind, 5] <- pred.of[3,2]

ind <- which((submission[,1]=="600MPE" & submission[,2]=="PF-3084014"))
submission[ind, 5] <- pred.of[1,2]

ind <- which((submission[,1]=="HCC1954" & submission[,2]=="PF-3084014"))
submission[ind, 5] <- pred.of[5,2]

ind <- which((submission[,1]=="SKBR3" & submission[,2]=="PF-3084014"))
submission[ind, 5] <- pred.of[14,2]

ind <- which((submission[,1]=="MCF12A" & submission[,2]=="PF-3084014"))
submission[ind, 5] <- pred.of[9,2]

ind <- which((submission[,1]=="HCC3153" & submission[,2]=="PF-3084014"))
submission[ind, 5] <- pred.of[6,2]

ind <- which((submission[,1]=="MDAMB157" & submission[,2]=="PF-3084014"))
submission[ind, 5] <- pred.of[11,2]

ind <- which((submission[,1]=="LY2" & submission[,2]=="PF-3084014"))
submission[ind, 5] <- pred.of[7,2]

ind <- which((submission[,1]=="AU565" & submission[,2]=="PF-3084014"))
submission[ind, 5] <- pred.of[2,2]

ind <- which((submission[,1]=="MCF10A" & submission[,2]=="PF-3084014"))
submission[ind, 5] <- pred.of[8,2]
```


#drug10
```{r}
#running of selected model
pred.of = predict(shire10,test,type='prob')

#write into the submission file

ind <- which((submission[,1]=="HCC1187" & submission[,2]=="PF-3814735"))
submission[ind, 5] <- pred.of[4,2]

ind <- which((submission[,1]=="MCF7" & submission[,2]=="PF-3814735"))
submission[ind, 5] <- pred.of[10,2]

ind <- which((submission[,1]=="MDAMB361" & submission[,2]=="PF-3814735"))
submission[ind, 5] <- pred.of[13,2]

ind <- which((submission[,1]=="MDAMB231" & submission[,2]=="PF-3814735"))
submission[ind, 5] <- pred.of[12,2]

ind <- which((submission[,1]=="BT549" & submission[,2]=="PF-3814735"))
submission[ind, 5] <- pred.of[3,2]

ind <- which((submission[,1]=="600MPE" & submission[,2]=="PF-3814735"))
submission[ind, 5] <- pred.of[1,2]

ind <- which((submission[,1]=="HCC1954" & submission[,2]=="PF-3814735"))
submission[ind, 5] <- pred.of[5,2]

ind <- which((submission[,1]=="SKBR3" & submission[,2]=="PF-3814735"))
submission[ind, 5] <- pred.of[14,2]

ind <- which((submission[,1]=="MCF12A" & submission[,2]=="PF-3814735"))
submission[ind, 5] <- pred.of[9,2]

ind <- which((submission[,1]=="HCC3153" & submission[,2]=="PF-3814735"))
submission[ind, 5] <- pred.of[6,2]

ind <- which((submission[,1]=="MDAMB157" & submission[,2]=="PF-3814735"))
submission[ind, 5] <- pred.of[11,2]

ind <- which((submission[,1]=="LY2" & submission[,2]=="PF-3814735"))
submission[ind, 5] <- pred.of[7,2]

ind <- which((submission[,1]=="AU565" & submission[,2]=="PF-3814735"))
submission[ind, 5] <- pred.of[2,2]

ind <- which((submission[,1]=="MCF10A" & submission[,2]=="PF-3814735"))
submission[ind, 5] <- pred.of[8,2]
```


#drug11
```{r}
#running of selected model
pred.of = predict(shire11,test,type='prob')


#write into the submission file

ind <- which((submission[,1]=="HCC1187" & submission[,2]=="PF-4691502"))
submission[ind, 5] <- pred.of[4,2]

ind <- which((submission[,1]=="MCF7" & submission[,2]=="PF-4691502"))
submission[ind, 5] <- pred.of[10,2]

ind <- which((submission[,1]=="MDAMB361" & submission[,2]=="PF-4691502"))
submission[ind, 5] <- pred.of[13,2]

ind <- which((submission[,1]=="MDAMB231" & submission[,2]=="PF-4691502"))
submission[ind, 5] <- pred.of[12,2]

ind <- which((submission[,1]=="BT549" & submission[,2]=="PF-4691502"))
submission[ind, 5] <- pred.of[3,2]

ind <- which((submission[,1]=="600MPE" & submission[,2]=="PF-4691502"))
submission[ind, 5] <- pred.of[1,2]

ind <- which((submission[,1]=="HCC1954" & submission[,2]=="PF-4691502"))
submission[ind, 5] <- pred.of[5,2]

ind <- which((submission[,1]=="SKBR3" & submission[,2]=="PF-4691502"))
submission[ind, 5] <- pred.of[14,2]

ind <- which((submission[,1]=="MCF12A" & submission[,2]=="PF-4691502"))
submission[ind, 5] <- pred.of[9,2]

ind <- which((submission[,1]=="HCC3153" & submission[,2]=="PF-4691502"))
submission[ind, 5] <- pred.of[6,2]

ind <- which((submission[,1]=="MDAMB157" & submission[,2]=="PF-4691502"))
submission[ind, 5] <- pred.of[11,2]

ind <- which((submission[,1]=="LY2" & submission[,2]=="PF-4691502"))
submission[ind, 5] <- pred.of[7,2]

ind <- which((submission[,1]=="AU565" & submission[,2]=="PF-4691502"))
submission[ind, 5] <- pred.of[2,2]

ind <- which((submission[,1]=="MCF10A" & submission[,2]=="PF-4691502"))
submission[ind, 5] <- pred.of[8,2]
```


#drug12
```{r}
#running of selected model
pred.of = predict(shire12,test,type='prob')

#write into the submission file

ind <- which((submission[,1]=="HCC1187" & submission[,2]=="Paclitaxel"))
submission[ind, 5] <- pred.of[4,2]

ind <- which((submission[,1]=="MCF7" & submission[,2]=="Paclitaxel"))
submission[ind, 5] <- pred.of[10,2]

ind <- which((submission[,1]=="MDAMB361" & submission[,2]=="Paclitaxel"))
submission[ind, 5] <- pred.of[13,2]

ind <- which((submission[,1]=="MDAMB231" & submission[,2]=="Paclitaxel"))
submission[ind, 5] <- pred.of[12,2]

ind <- which((submission[,1]=="BT549" & submission[,2]=="Paclitaxel"))
submission[ind, 5] <- pred.of[3,2]

ind <- which((submission[,1]=="600MPE" & submission[,2]=="Paclitaxel"))
submission[ind, 5] <- pred.of[1,2]

ind <- which((submission[,1]=="HCC1954" & submission[,2]=="Paclitaxel"))
submission[ind, 5] <- pred.of[5,2]

ind <- which((submission[,1]=="SKBR3" & submission[,2]=="Paclitaxel"))
submission[ind, 5] <- pred.of[14,2]

ind <- which((submission[,1]=="MCF12A" & submission[,2]=="Paclitaxel"))
submission[ind, 5] <- pred.of[9,2]

ind <- which((submission[,1]=="HCC3153" & submission[,2]=="Paclitaxel"))
submission[ind, 5] <- pred.of[6,2]

ind <- which((submission[,1]=="MDAMB157" & submission[,2]=="Paclitaxel"))
submission[ind, 5] <- pred.of[11,2]

ind <- which((submission[,1]=="LY2" & submission[,2]=="Paclitaxel"))
submission[ind, 5] <- pred.of[7,2]

ind <- which((submission[,1]=="AU565" & submission[,2]=="Paclitaxel"))
submission[ind, 5] <- pred.of[2,2]

ind <- which((submission[,1]=="MCF10A" & submission[,2]=="Paclitaxel"))
submission[ind, 5] <- pred.of[8,2]
```

#write to csv
```{r}
kaggel<-data.frame(submission$id , submission$train_accuracy)
kaggel
write.csv(kaggel,file="trees1%.csv")
```
```

