---
title: "forrest prediction"
output: html_document
---
Write up for forests 

Random forest was one of the methods we chose to use to approach this problem. There were several reasons behind this decision the size of the data left something to be desired and it was felt that random forest would help with this factor, as well as the general predictive power of random forests being very strong. We were also required to use a bagging or boosting in out model and random forest is a bagging method. By utilizing the stochastic complexity of the model, we were given the forests helped create a higher prediction score, we then boosted by taking only the best forests and using them for our final model. It should also to be noted that the effectiveness of this method was noted in the original paper linked to the data.

This task is accomplished by taking the test data and filtering it into three categories based on variance. A variance threshold of 0.5 that incapsulates the top 20% most variant genes, a variance threshold of 1 that incapsulates the top 10% most variant genes, a variance threshold of 1.5 that incapsulates the top 5% most variant genes, and a variance threshold of 3.5 that incapsulates the top 1% most variant genes. The decision was made for these thresholds after not having enough computing power to train on the entire dataset these filters were applied because it was felt that they would capture enough of the important variables present in the file to build a decent predictive model. After the training set is filtered into its different category’s Then each of the variant files has a drug column applied to it one at a time so the first set of models uses drug one and so on. This set of four models is then run an initial time to get a baseline with the default settings of the randomforest() function First the trees are optimized by seeing the error rate per tree and the overall out of bag rate for each model the graphing allows the user to see where the trees begin to level out. Once this step is complete using the new tree count a loop is run where each model is created 20 times with varying splits from 1-20. From this the error rates for each model is displayed and the one with the lowest is chosen as the split number for the model. This new split number and tree number are then fed back into the randomforest() function and the final model is created for that drug/variance level combination. This step is reproduced 12 times once for each drug resulting in the creation of 48 over all models. From these models the model with the lowest out of bag error rate was chosen to move on to the next step. After the information from both the fangorn and shire files has been completed each of the models is compared to one another for each drug and the one with the lowest oob error rate is selected to be used in the final model. If a tie occurs the lowest drug variance is chosen this is because when run multiple ways it seemed as though the lower variance rates yielded better results over all. Then the predict function is run on each of the drug models and out puts a probability matrix for each of the drug cell line combinations this is saved under its drug cell line combination to a csv file named submission that is written out and used to submit to kaggel.

The final model that was submitted to Kaggle had the following parameters. 6 drugs use their 1% variance models,2 drugs use their 5% models, 3 drugs use their 10% models and 1 drug uses its 20% model. This combination allowed for the largest score when applied to the testing set, and as such was chosen as the submission set. Changing tie metric by rounding up rather than down when picking between OOB rate only decreased accuracy. 

Over all on the testing data that Kaggle provided prior to releasing the final 40% of the data the model preformed rather well, however there is the possibility that it is over fit to the testing data and not as accurate as it seems to be on a wider set of data due to the high level of variance filtering applied prior to forest creation. Also due to the nature of the data used to create the models the model will likely not be very scalable to a new population as the sample set was very small, as well as most of the subtypes being luminal this will likely not be able to be accuratly extrapolated to a larger dataset let alone the public. 





#Document notes
This is the document that writes the final submission section for the kaggel competition. After the information from both the fangorn and shire files has been completed each of the models is compared to one another for each drug and the one with the lowest oob error rate is selected to be used in the final model. If a tie occurs the lowest drug variance is chosen this is because when run multiple ways it seemed as though the lower variance rates yielded better results over all. Then the predict function is run on each of the drug models and out puts a probability matrix for each of the drug cell line combinations this is saved under its drug cell line combination to a csv file named submission that is written out and used to submit to kaggel. 

this version is the best out put from the project using the following breakdown of variance models 
1% variance models = 6

5% models = 2

10% models = 3

20% models = 1

```{r}
sessionInfo()
```

```{r}
set.seed(25000)
library(tidyverse)
library(ggplot2)
library(cowplot)
library(randomForest)
library(parallel)
library(skimr)
library(broom)
library(janitor)
library(dplyr)
library(readr)
library(genefilter)
#library(parLapply)

```


```{r}
#Read in the cleaned expression data
expression <- as.data.frame((read.table("../data/clean_expression.txt", row.names=1 )))
rownames(expression)[1] <- '184A1'# Rename the only integer name

# Read in the subtype data
subtypes <- read_tsv("../data/clean_subtypes.txt")

# Read in the truth set
truth_set <-  as.data.frame((read.table("../data/clean_training_answers.txt", row.names=1 )))


# Create merged feature set
featureSet<-cbind(subtypes[,2],t(expression))

#read in the submission table
submission<-as.data.frame((read.csv("../data/scoring_and_test_set_id_mappings.csv")))
submission[ , 'train_accuracy'] <- NA

#read in the test sethead
test<-as.data.frame(t(read.table("../data/clean_test_expression.txt", row.names=1 )))
test<-clean_names(test)
```

```{r}
expVar <- (rowVars(expression))
hist(expVar)
expVar <- as.data.frame(expVar)
names(expVar) <- c('variance')

paste('max variance:', max(expVar[,1]))
paste('min variance:', min(expVar[,1]))

#top 20 of genes
expVar %>% count((variance > '0.5'))
top20 <- expVar$variance > 0.5 
root20 <- expression[top20,]
root20<-data.frame(t(root20))
dim(root20)




#top 10% of genes
expVar %>% count((variance > '1'))
top10 <- expVar$variance > 1 
root10 <- expression[top10,]
root10<-data.frame(t(root10))
dim(root10)




#top 5% of genes
expVar %>% count((variance > '1.5'))
top5 <- expVar$variance > 1.5 
root5 <- expression[top5,]
root5<-data.frame(t(root5))
dim(root5)

#top 1% of genes 
#top 1 of genes
expVar %>% count((variance > '3.5'))
top <- expVar$variance > 3.5
root <- expression[top,]
root<-data.frame(t(root))
dim(root)


```
```{r}
expVar<-clean_names(expVar)
#subsetting the test set by the different varient calls
#20%
top20 <- expVar$variance > 0.5 
test20<- test[,(top20)]
test20<-clean_names(test20)
colnames(test20)[1]<-"x184a1"

#10%
top10 <- expVar$variance > 1 
test10<- test[,(top10)]
test10<-clean_names(test10)
colnames(test10)[1]<-"x184a1"
#5%
top5<- expVar$variance > 1.5 
test5<- test[,(top5)]
colnames(test5)[1]<-"x184a1"

top <- expVar$variance > 3.5 
test<- test[,(top)]
test<-clean_names(test)
colnames(test)[1]<-"x184a1"
```

#forest 1
```{r}
#attaching the drug data
tree1<-cbind(drug=truth_set[,1],root)
tree1<-clean_names(tree1)
tree1$drug<-factor(tree1$drug)

```

```{r}
#creating the forest
set.seed(1)
shire <- randomForest( drug∼.,data=tree1  ,mtry=2,ntree=1000)
shire

```


```{r}

#uses the 1% variant forest because it had the lowest OOB 
pred.of = predict(shire,test,type='prob')


#write into the submission file

ind <- which((submission[,1]=="HCC1187" & submission[,2]=="CGC-11047"))
submission[ind, 5] <- pred.of[4,2]

ind <- which((submission[,1]=="MCF7" & submission[,2]=="CGC-11047"))
submission[ind, 5] <- pred.of[10,2]

ind <- which((submission[,1]=="MDAMB361" & submission[,2]=="CGC-11047"))
submission[ind, 5] <- pred.of[13,2]

ind <- which((submission[,1]=="MDAMB231" & submission[,2]=="CGC-11047"))
submission[ind, 5] <- pred.of[12,2]

ind <- which((submission[,1]=="BT549" & submission[,2]=="CGC-11047"))
submission[ind, 5] <- pred.of[3,2]

ind <- which((submission[,1]=="600MPE" & submission[,2]=="CGC-11047"))
submission[ind, 5] <- pred.of[1,2]

ind <- which((submission[,1]=="HCC1954" & submission[,2]=="CGC-11047"))
submission[ind, 5] <- pred.of[5,2]

ind <- which((submission[,1]=="SKBR3" & submission[,2]=="CGC-11047"))
submission[ind, 5] <- pred.of[14,2]

ind <- which((submission[,1]=="MCF12A" & submission[,2]=="CGC-11047"))
submission[ind, 5] <- pred.of[9,2]

ind <- which((submission[,1]=="HCC3153" & submission[,2]=="CGC-11047"))
submission[ind, 5] <- pred.of[6,2]

ind <- which((submission[,1]=="MDAMB157" & submission[,2]=="CGC-11047"))
submission[ind, 5] <- pred.of[11,2]

ind <- which((submission[,1]=="LY2" & submission[,2]=="CGC-11047"))
submission[ind, 5] <- pred.of[7,2]

ind <- which((submission[,1]=="AU565" & submission[,2]=="CGC-11047"))
submission[ind, 5] <- pred.of[2,2]

ind <- which((submission[,1]=="MCF10A" & submission[,2]=="CGC-11047"))
submission[ind, 5] <- pred.of[8,2]


```

#forest 2
```{r}
#attaching the drug data
tree2<-cbind(drug=truth_set[,2],root)
tree2<-clean_names(tree2)
tree2$drug<-factor(tree2$drug)
```

```{r}
#forest creation
set.seed(1)
shire2 <- randomForest( drug∼.,data=tree2  ,mtry=2,ntree=500)
shire2
```

```{r}
#uses the 1 % variant forest because it was tied for lowest oob 
pred.of = predict(shire2,test,type='prob')

#write into the submission file

ind <- which((submission[,1]=="HCC1187" & submission[,2]=="Carboplatin"))
submission[ind, 5] <- pred.of[4,2]

ind <- which((submission[,1]=="MCF7" & submission[,2]=="Carboplatin"))
submission[ind, 5] <- pred.of[10,2]

ind <- which((submission[,1]=="MDAMB361" & submission[,2]=="Carboplatin"))
submission[ind, 5] <- pred.of[13,2]

ind <- which((submission[,1]=="MDAMB231" & submission[,2]=="Carboplatin"))
submission[ind, 5] <- pred.of[12,2]

ind <- which((submission[,1]=="BT549" & submission[,2]=="Carboplatin"))
submission[ind, 5] <- pred.of[3,2]

ind <- which((submission[,1]=="600MPE" & submission[,2]=="Carboplatin"))
submission[ind, 5] <- pred.of[1,2]

ind <- which((submission[,1]=="HCC1954" & submission[,2]=="Carboplatin"))
submission[ind, 5] <- pred.of[5,2]

ind <- which((submission[,1]=="SKBR3" & submission[,2]=="Carboplatin"))
submission[ind, 5] <- pred.of[14,2]

ind <- which((submission[,1]=="MCF12A" & submission[,2]=="Carboplatin"))
submission[ind, 5] <- pred.of[9,2]

ind <- which((submission[,1]=="HCC3153" & submission[,2]=="Carboplatin"))
submission[ind, 5] <- pred.of[6,2]

ind <- which((submission[,1]=="MDAMB157" & submission[,2]=="Carboplatin"))
submission[ind, 5] <- pred.of[11,2]

ind <- which((submission[,1]=="LY2" & submission[,2]=="Carboplatin"))
submission[ind, 5] <- pred.of[7,2]

ind <- which((submission[,1]=="AU565" & submission[,2]=="Carboplatin"))
submission[ind, 5] <- pred.of[2,2]

ind <- which((submission[,1]=="MCF10A" & submission[,2]=="Carboplatin"))
submission[ind, 5] <- pred.of[8,2]


```

#forest 3
```{r}
#attaching the drug data
tree3<-cbind(drug=truth_set[,3],root)
tree3<-clean_names(tree3)
tree3$drug<-factor(tree3$drug)
```

```{r}
#forest creation
set.seed(1)
shire3 <- randomForest( drug∼.,data=tree3  ,mtry=9,ntree=500)
shire3
```

```{r}
#used 1%because it had the lowest oob error rate
pred.of = predict(shire3,test,type='prob')


#write into the submission file

ind <- which((submission[,1]=="HCC1187" & submission[,2]=="Cisplatin"))
submission[ind, 5] <- pred.of[4,2]

ind <- which((submission[,1]=="MCF7" & submission[,2]=="Cisplatin"))
submission[ind, 5] <- pred.of[10,2]

ind <- which((submission[,1]=="MDAMB361" & submission[,2]=="Cisplatin"))
submission[ind, 5] <- pred.of[13,2]

ind <- which((submission[,1]=="MDAMB231" & submission[,2]=="Cisplatin"))
submission[ind, 5] <- pred.of[12,2]

ind <- which((submission[,1]=="BT549" & submission[,2]=="Cisplatin"))
submission[ind, 5] <- pred.of[3,2]

ind <- which((submission[,1]=="600MPE" & submission[,2]=="Cisplatin"))
submission[ind, 5] <- pred.of[1,2]

ind <- which((submission[,1]=="HCC1954" & submission[,2]=="Cisplatin"))
submission[ind, 5] <- pred.of[5,2]

ind <- which((submission[,1]=="SKBR3" & submission[,2]=="Cisplatin"))
submission[ind, 5] <- pred.of[14,2]

ind <- which((submission[,1]=="MCF12A" & submission[,2]=="Cisplatin"))
submission[ind, 5] <- pred.of[9,2]

ind <- which((submission[,1]=="HCC3153" & submission[,2]=="Cisplatin"))
submission[ind, 5] <- pred.of[6,2]

ind <- which((submission[,1]=="MDAMB157" & submission[,2]=="Cisplatin"))
submission[ind, 5] <- pred.of[11,2]

ind <- which((submission[,1]=="LY2" & submission[,2]=="Cisplatin"))
submission[ind, 5] <- pred.of[7,2]

ind <- which((submission[,1]=="AU565" & submission[,2]=="Cisplatin"))
submission[ind, 5] <- pred.of[2,2]

ind <- which((submission[,1]=="MCF10A" & submission[,2]=="Cisplatin"))
submission[ind, 5] <- pred.of[8,2]
```


#forest 4
```{r}
##attaching the drug data
tree405<-cbind(drug=truth_set[,4],root5)
tree405<-clean_names(tree405)
tree405$drug<-factor(tree405$drug)
```

```{r}
#forest creation
set.seed(1)

oldForest4 <- randomForest( drug∼.,data=tree405  ,mtry=2,ntree=1000)
oldForest4
```

```{r}
#used 5%because it was tied for the lowest oob error rate
pred.of = predict(oldForest4,test5,type='prob')


#write into the submission file

ind <- which((submission[,1]=="HCC1187" & submission[,2]=="GSK1070916"))
submission[ind, 5] <- pred.of[4,2]

ind <- which((submission[,1]=="MCF7" & submission[,2]=="GSK1070916"))
submission[ind, 5] <- pred.of[10,2]

ind <- which((submission[,1]=="MDAMB361" & submission[,2]=="GSK1070916"))
submission[ind, 5] <- pred.of[13,2]

ind <- which((submission[,1]=="MDAMB231" & submission[,2]=="GSK1070916"))
submission[ind, 5] <- pred.of[12,2]

ind <- which((submission[,1]=="BT549" & submission[,2]=="GSK1070916"))
submission[ind, 5] <- pred.of[3,2]

ind <- which((submission[,1]=="600MPE" & submission[,2]=="GSK1070916"))
submission[ind, 5] <- pred.of[1,2]

ind <- which((submission[,1]=="HCC1954" & submission[,2]=="GSK1070916"))
submission[ind, 5] <- pred.of[5,2]

ind <- which((submission[,1]=="SKBR3" & submission[,2]=="GSK1070916"))
submission[ind, 5] <- pred.of[14,2]

ind <- which((submission[,1]=="MCF12A" & submission[,2]=="GSK1070916"))
submission[ind, 5] <- pred.of[9,2]

ind <- which((submission[,1]=="HCC3153" & submission[,2]=="GSK1070916"))
submission[ind, 5] <- pred.of[6,2]

ind <- which((submission[,1]=="MDAMB157" & submission[,2]=="GSK1070916"))
submission[ind, 5] <- pred.of[11,2]

ind <- which((submission[,1]=="LY2" & submission[,2]=="GSK1070916"))
submission[ind, 5] <- pred.of[7,2]

ind <- which((submission[,1]=="AU565" & submission[,2]=="GSK1070916"))
submission[ind, 5] <- pred.of[2,2]

ind <- which((submission[,1]=="MCF10A" & submission[,2]=="GSK1070916"))
submission[ind, 5] <- pred.of[8,2]
```

#forest 5
```{r}
#attaching the drug data
tree505<-cbind(drug=truth_set[,5],root5)
tree505<-clean_names(tree505)
tree505$drug<-factor(tree505$drug)
```

```{r}
#creating the forest
set.seed(1)
oldForest5 <- randomForest( drug∼.,data=tree505  ,mtry=8,ntree=500)
oldForest5
```

```{r}
#used 5%because it was tied for the lowest oob error rate
pred.of = predict(oldForest5,test5,type='prob')

#write into the submission file

ind <- which((submission[,1]=="HCC1187" & submission[,2]=="GSK1120212"))
submission[ind, 5] <- pred.of[4,2]

ind <- which((submission[,1]=="MCF7" & submission[,2]=="GSK1120212"))
submission[ind, 5] <- pred.of[10,2]

ind <- which((submission[,1]=="MDAMB361" & submission[,2]=="GSK1120212"))
submission[ind, 5] <- pred.of[13,2]

ind <- which((submission[,1]=="MDAMB231" & submission[,2]=="GSK1120212"))
submission[ind, 5] <- pred.of[12,2]

ind <- which((submission[,1]=="BT549" & submission[,2]=="GSK1120212"))
submission[ind, 5] <- pred.of[3,2]

ind <- which((submission[,1]=="600MPE" & submission[,2]=="GSK1120212"))
submission[ind, 5] <- pred.of[1,2]

ind <- which((submission[,1]=="HCC1954" & submission[,2]=="GSK1120212"))
submission[ind, 5] <- pred.of[5,2]

ind <- which((submission[,1]=="SKBR3" & submission[,2]=="GSK1120212"))
submission[ind, 5] <- pred.of[14,2]

ind <- which((submission[,1]=="MCF12A" & submission[,2]=="GSK1120212"))
submission[ind, 5] <- pred.of[9,2]

ind <- which((submission[,1]=="HCC3153" & submission[,2]=="GSK1120212"))
submission[ind, 5] <- pred.of[6,2]

ind <- which((submission[,1]=="MDAMB157" & submission[,2]=="GSK1120212"))
submission[ind, 5] <- pred.of[11,2]

ind <- which((submission[,1]=="LY2" & submission[,2]=="GSK1120212"))
submission[ind, 5] <- pred.of[7,2]

ind <- which((submission[,1]=="AU565" & submission[,2]=="GSK1120212"))
submission[ind, 5] <- pred.of[2,2]

ind <- which((submission[,1]=="MCF10A" & submission[,2]=="GSK1120212"))
submission[ind, 5] <- pred.of[8,2]
```

#forest 6
```{r}
#attaching the drug data
tree6<-cbind(drug=truth_set[,6],root)
tree6<-clean_names(tree6)
tree6$drug<-factor(tree6$drug)
```

```{r}
#forest creation
set.seed(1)
shire6 <- randomForest( drug∼.,data=tree6  ,mtry=5,ntree=1000)
shire6
```

```{r}
#used 1%because it had the lowest oob error rate
pred.of = predict(shire6,test,type='prob')

#write into the submission file

ind <- which((submission[,1]=="HCC1187" & submission[,2]=="GSK461364"))
submission[ind, 5] <- pred.of[4,2]

ind <- which((submission[,1]=="MCF7" & submission[,2]=="GSK461364"))
submission[ind, 5] <- pred.of[10,2]

ind <- which((submission[,1]=="MDAMB361" & submission[,2]=="GSK461364"))
submission[ind, 5] <- pred.of[13,2]

ind <- which((submission[,1]=="MDAMB231" & submission[,2]=="GSK461364"))
submission[ind, 5] <- pred.of[12,2]

ind <- which((submission[,1]=="BT549" & submission[,2]=="GSK461364"))
submission[ind, 5] <- pred.of[3,2]

ind <- which((submission[,1]=="600MPE" & submission[,2]=="GSK461364"))
submission[ind, 5] <- pred.of[1,2]

ind <- which((submission[,1]=="HCC1954" & submission[,2]=="GSK461364"))
submission[ind, 5] <- pred.of[5,2]

ind <- which((submission[,1]=="SKBR3" & submission[,2]=="GSK461364"))
submission[ind, 5] <- pred.of[14,2]

ind <- which((submission[,1]=="MCF12A" & submission[,2]=="GSK461364"))
submission[ind, 5] <- pred.of[9,2]

ind <- which((submission[,1]=="HCC3153" & submission[,2]=="GSK461364"))
submission[ind, 5] <- pred.of[6,2]

ind <- which((submission[,1]=="MDAMB157" & submission[,2]=="GSK461364"))
submission[ind, 5] <- pred.of[11,2]

ind <- which((submission[,1]=="LY2" & submission[,2]=="GSK461364"))
submission[ind, 5] <- pred.of[7,2]

ind <- which((submission[,1]=="AU565" & submission[,2]=="GSK461364"))
submission[ind, 5] <- pred.of[2,2]

ind <- which((submission[,1]=="MCF10A" & submission[,2]=="GSK461364"))
submission[ind, 5] <- pred.of[8,2]
```

#forest 7
```{r}
#attaching the drug data
tree7<-cbind(drug=truth_set[,7],root)
tree7<-clean_names(tree7)
tree7$drug<-factor(tree7$drug)

```

```{r}
#forest creation
set.seed(1)
shire7 <- randomForest( drug∼.,data=tree7  ,mtry=6,ntree=3000)
shire7
```

```{r}
#used 1%because it was tied lowest oob error rate
pred.of = predict(shire7,test,type='prob')

#write into the submission file

ind <- which((submission[,1]=="HCC1187" & submission[,2]=="Geldanamycin"))
submission[ind, 5] <- pred.of[4,2]

ind <- which((submission[,1]=="MCF7" & submission[,2]=="Geldanamycin"))
submission[ind, 5] <- pred.of[10,2]

ind <- which((submission[,1]=="MDAMB361" & submission[,2]=="Geldanamycin"))
submission[ind, 5] <- pred.of[13,2]

ind <- which((submission[,1]=="MDAMB231" & submission[,2]=="Geldanamycin"))
submission[ind, 5] <- pred.of[12,2]

ind <- which((submission[,1]=="BT549" & submission[,2]=="Geldanamycin"))
submission[ind, 5] <- pred.of[3,2]

ind <- which((submission[,1]=="600MPE" & submission[,2]=="Geldanamycin"))
submission[ind, 5] <- pred.of[1,2]

ind <- which((submission[,1]=="HCC1954" & submission[,2]=="Geldanamycin"))
submission[ind, 5] <- pred.of[5,2]

ind <- which((submission[,1]=="SKBR3" & submission[,2]=="Geldanamycin"))
submission[ind, 5] <- pred.of[14,2]

ind <- which((submission[,1]=="MCF12A" & submission[,2]=="Geldanamycin"))
submission[ind, 5] <- pred.of[9,2]

ind <- which((submission[,1]=="HCC3153" & submission[,2]=="Geldanamycin"))
submission[ind, 5] <- pred.of[6,2]

ind <- which((submission[,1]=="MDAMB157" & submission[,2]=="Geldanamycin"))
submission[ind, 5] <- pred.of[11,2]

ind <- which((submission[,1]=="LY2" & submission[,2]=="Geldanamycin"))
submission[ind, 5] <- pred.of[7,2]

ind <- which((submission[,1]=="AU565" & submission[,2]=="Geldanamycin"))
submission[ind, 5] <- pred.of[2,2]

ind <- which((submission[,1]=="MCF10A" & submission[,2]=="Geldanamycin"))
submission[ind, 5] <- pred.of[8,2]

```

#forest 8
```{r}
#attaching the drug data
tree810<-cbind(drug=truth_set[,8],root10)
tree810<-clean_names(tree810)
tree810$drug<-factor(tree810$drug)

```

```{r}
#forest creation
set.seed(1)
#assuming that 0.20 is the lowest
mirkwood8 <- randomForest( drug∼.,data=tree810  ,mtry=4,ntree=1000)
mirkwood8

```

```{r}
#used 10%because it had the lowest oob error rate
pred.of = predict(mirkwood8,test10,type='prob')

#write into the submission file

ind <- which((submission[,1]=="HCC1187" & submission[,2]=="Oxaliplatin"))
submission[ind, 5] <- pred.of[4,2]

ind <- which((submission[,1]=="MCF7" & submission[,2]=="Oxaliplatin"))
submission[ind, 5] <- pred.of[10,2]

ind <- which((submission[,1]=="MDAMB361" & submission[,2]=="Oxaliplatin"))
submission[ind, 5] <- pred.of[13,2]

ind <- which((submission[,1]=="MDAMB231" & submission[,2]=="Oxaliplatin"))
submission[ind, 5] <- pred.of[12,2]

ind <- which((submission[,1]=="BT549" & submission[,2]=="Oxaliplatin"))
submission[ind, 5] <- pred.of[3,2]

ind <- which((submission[,1]=="600MPE" & submission[,2]=="Oxaliplatin"))
submission[ind, 5] <- pred.of[1,2]

ind <- which((submission[,1]=="HCC1954" & submission[,2]=="Oxaliplatin"))
submission[ind, 5] <- pred.of[5,2]

ind <- which((submission[,1]=="SKBR3" & submission[,2]=="Oxaliplatin"))
submission[ind, 5] <- pred.of[14,2]

ind <- which((submission[,1]=="MCF12A" & submission[,2]=="Oxaliplatin"))
submission[ind, 5] <- pred.of[9,2]

ind <- which((submission[,1]=="HCC3153" & submission[,2]=="Oxaliplatin"))
submission[ind, 5] <- pred.of[6,2]

ind <- which((submission[,1]=="MDAMB157" & submission[,2]=="Oxaliplatin"))
submission[ind, 5] <- pred.of[11,2]

ind <- which((submission[,1]=="LY2" & submission[,2]=="Oxaliplatin"))
submission[ind, 5] <- pred.of[7,2]

ind <- which((submission[,1]=="AU565" & submission[,2]=="Oxaliplatin"))
submission[ind, 5] <- pred.of[2,2]

ind <- which((submission[,1]=="MCF10A" & submission[,2]=="Oxaliplatin"))
submission[ind, 5] <- pred.of[8,2]

```

#forest 9
```{r}
#attaching the drug data
tree9<-cbind(drug=truth_set[,9],root)
tree9<-clean_names(tree9)
tree9$drug<-factor(tree9$drug)

```

```{r}
#forest creation
set.seed(1)
shire9 <- randomForest( drug∼.,data=tree9  ,mtry=3,ntree=1000)
shire9
```

```{r}
#used 1%because it was tied for the lowest oob error rate
pred.of = predict(shire9,test,type='prob')

#write into the submission file

ind <- which((submission[,1]=="HCC1187" & submission[,2]=="PF-3084014"))
submission[ind, 5] <- pred.of[4,2]

ind <- which((submission[,1]=="MCF7" & submission[,2]=="PF-3084014"))
submission[ind, 5] <- pred.of[10,2]

ind <- which((submission[,1]=="MDAMB361" & submission[,2]=="PF-3084014"))
submission[ind, 5] <- pred.of[13,2]

ind <- which((submission[,1]=="MDAMB231" & submission[,2]=="PF-3084014"))
submission[ind, 5] <- pred.of[12,2]

ind <- which((submission[,1]=="BT549" & submission[,2]=="PF-3084014"))
submission[ind, 5] <- pred.of[3,2]

ind <- which((submission[,1]=="600MPE" & submission[,2]=="PF-3084014"))
submission[ind, 5] <- pred.of[1,2]

ind <- which((submission[,1]=="HCC1954" & submission[,2]=="PF-3084014"))
submission[ind, 5] <- pred.of[5,2]

ind <- which((submission[,1]=="SKBR3" & submission[,2]=="PF-3084014"))
submission[ind, 5] <- pred.of[14,2]

ind <- which((submission[,1]=="MCF12A" & submission[,2]=="PF-3084014"))
submission[ind, 5] <- pred.of[9,2]

ind <- which((submission[,1]=="HCC3153" & submission[,2]=="PF-3084014"))
submission[ind, 5] <- pred.of[6,2]

ind <- which((submission[,1]=="MDAMB157" & submission[,2]=="PF-3084014"))
submission[ind, 5] <- pred.of[11,2]

ind <- which((submission[,1]=="LY2" & submission[,2]=="PF-3084014"))
submission[ind, 5] <- pred.of[7,2]

ind <- which((submission[,1]=="AU565" & submission[,2]=="PF-3084014"))
submission[ind, 5] <- pred.of[2,2]

ind <- which((submission[,1]=="MCF10A" & submission[,2]=="PF-3084014"))
submission[ind, 5] <- pred.of[8,2]
```

#forest 10
```{r}
##attaching the drug data
tree1010<-cbind(drug=truth_set[,10],root10)
tree1010<-clean_names(tree1010)
tree1010$drug<-factor(tree1010$drug)

```

```{r}
set.seed(1)
#forest creation
#assuming that 0.20 is the lowest
mirkwood10 <- randomForest( drug∼.,data=tree1010  ,mtry=11,ntree=500)
mirkwood10

```

```{r}
#used 10%because it was the lowest oob error rate
pred.of = predict(mirkwood10,test10,type='prob')


#write into the submission file

ind <- which((submission[,1]=="HCC1187" & submission[,2]=="PF-3814735"))
submission[ind, 5] <- pred.of[4,2]

ind <- which((submission[,1]=="MCF7" & submission[,2]=="PF-3814735"))
submission[ind, 5] <- pred.of[10,2]

ind <- which((submission[,1]=="MDAMB361" & submission[,2]=="PF-3814735"))
submission[ind, 5] <- pred.of[13,2]

ind <- which((submission[,1]=="MDAMB231" & submission[,2]=="PF-3814735"))
submission[ind, 5] <- pred.of[12,2]

ind <- which((submission[,1]=="BT549" & submission[,2]=="PF-3814735"))
submission[ind, 5] <- pred.of[3,2]

ind <- which((submission[,1]=="600MPE" & submission[,2]=="PF-3814735"))
submission[ind, 5] <- pred.of[1,2]

ind <- which((submission[,1]=="HCC1954" & submission[,2]=="PF-3814735"))
submission[ind, 5] <- pred.of[5,2]

ind <- which((submission[,1]=="SKBR3" & submission[,2]=="PF-3814735"))
submission[ind, 5] <- pred.of[14,2]

ind <- which((submission[,1]=="MCF12A" & submission[,2]=="PF-3814735"))
submission[ind, 5] <- pred.of[9,2]

ind <- which((submission[,1]=="HCC3153" & submission[,2]=="PF-3814735"))
submission[ind, 5] <- pred.of[6,2]

ind <- which((submission[,1]=="MDAMB157" & submission[,2]=="PF-3814735"))
submission[ind, 5] <- pred.of[11,2]

ind <- which((submission[,1]=="LY2" & submission[,2]=="PF-3814735"))
submission[ind, 5] <- pred.of[7,2]

ind <- which((submission[,1]=="AU565" & submission[,2]=="PF-3814735"))
submission[ind, 5] <- pred.of[2,2]

ind <- which((submission[,1]=="MCF10A" & submission[,2]=="PF-3814735"))
submission[ind, 5] <- pred.of[8,2]


```


#Forest 11
```{r}
#attaching the drug data
tree1120<-cbind(drug=truth_set[,11],root20)
tree1120<-clean_names(tree1120)
tree1120$drug<-factor(tree1120$drug)
```

```{r}
#Forest creation
set.seed(1)
#assuming that 0.40 is the lowest
fangorn11 <- randomForest( drug∼.,data=tree1120  ,mtry=6,ntree=500)
fangorn11
```

```{r}
#used 20%because it was the lowest oob error rate
pred.of = predict(fangorn11,test20,type='prob')

#write into the submission file

ind <- which((submission[,1]=="HCC1187" & submission[,2]=="PF-4691502"))
submission[ind, 5] <- pred.of[4,2]

ind <- which((submission[,1]=="MCF7" & submission[,2]=="PF-4691502"))
submission[ind, 5] <- pred.of[10,2]

ind <- which((submission[,1]=="MDAMB361" & submission[,2]=="PF-4691502"))
submission[ind, 5] <- pred.of[13,2]

ind <- which((submission[,1]=="MDAMB231" & submission[,2]=="PF-4691502"))
submission[ind, 5] <- pred.of[12,2]

ind <- which((submission[,1]=="BT549" & submission[,2]=="PF-4691502"))
submission[ind, 5] <- pred.of[3,2]

ind <- which((submission[,1]=="600MPE" & submission[,2]=="PF-4691502"))
submission[ind, 5] <- pred.of[1,2]

ind <- which((submission[,1]=="HCC1954" & submission[,2]=="PF-4691502"))
submission[ind, 5] <- pred.of[5,2]

ind <- which((submission[,1]=="SKBR3" & submission[,2]=="PF-4691502"))
submission[ind, 5] <- pred.of[14,2]

ind <- which((submission[,1]=="MCF12A" & submission[,2]=="PF-4691502"))
submission[ind, 5] <- pred.of[9,2]

ind <- which((submission[,1]=="HCC3153" & submission[,2]=="PF-4691502"))
submission[ind, 5] <- pred.of[6,2]

ind <- which((submission[,1]=="MDAMB157" & submission[,2]=="PF-4691502"))
submission[ind, 5] <- pred.of[11,2]

ind <- which((submission[,1]=="LY2" & submission[,2]=="PF-4691502"))
submission[ind, 5] <- pred.of[7,2]

ind <- which((submission[,1]=="AU565" & submission[,2]=="PF-4691502"))
submission[ind, 5] <- pred.of[2,2]

ind <- which((submission[,1]=="MCF10A" & submission[,2]=="PF-4691502"))
submission[ind, 5] <- pred.of[8,2]
```

#forest 12
```{r}
#attaching the drug data
tree1210<-cbind(drug=truth_set[,12],root10)
tree1210<-clean_names(tree1210)
tree1210$drug<-factor(tree1210$drug)
```

```{r}
#forest creation
set.seed(1)
#assuming that 0.40 is the lowest
mirkwood12 <- randomForest( drug∼.,data=tree1210  ,mtry=17,ntree=750)
mirkwood12

```

```{r}
#used 10%because it was the lowest oob error rate
pred.of = predict(mirkwood12,test10,type='prob')


#write into the submission file

ind <- which((submission[,1]=="HCC1187" & submission[,2]=="Paclitaxel"))
submission[ind, 5] <- pred.of[4,2]

ind <- which((submission[,1]=="MCF7" & submission[,2]=="Paclitaxel"))
submission[ind, 5] <- pred.of[10,2]

ind <- which((submission[,1]=="MDAMB361" & submission[,2]=="Paclitaxel"))
submission[ind, 5] <- pred.of[13,2]

ind <- which((submission[,1]=="MDAMB231" & submission[,2]=="Paclitaxel"))
submission[ind, 5] <- pred.of[12,2]

ind <- which((submission[,1]=="BT549" & submission[,2]=="Paclitaxel"))
submission[ind, 5] <- pred.of[3,2]

ind <- which((submission[,1]=="600MPE" & submission[,2]=="Paclitaxel"))
submission[ind, 5] <- pred.of[1,2]

ind <- which((submission[,1]=="HCC1954" & submission[,2]=="Paclitaxel"))
submission[ind, 5] <- pred.of[5,2]

ind <- which((submission[,1]=="SKBR3" & submission[,2]=="Paclitaxel"))
submission[ind, 5] <- pred.of[14,2]

ind <- which((submission[,1]=="MCF12A" & submission[,2]=="Paclitaxel"))
submission[ind, 5] <- pred.of[9,2]

ind <- which((submission[,1]=="HCC3153" & submission[,2]=="Paclitaxel"))
submission[ind, 5] <- pred.of[6,2]

ind <- which((submission[,1]=="MDAMB157" & submission[,2]=="Paclitaxel"))
submission[ind, 5] <- pred.of[11,2]

ind <- which((submission[,1]=="LY2" & submission[,2]=="Paclitaxel"))
submission[ind, 5] <- pred.of[7,2]

ind <- which((submission[,1]=="AU565" & submission[,2]=="Paclitaxel"))
submission[ind, 5] <- pred.of[2,2]

ind <- which((submission[,1]=="MCF10A" & submission[,2]=="Paclitaxel"))
submission[ind, 5] <- pred.of[8,2]
```


```{r}
kaggel<-data.frame(submission$id , submission$train_accuracy)
write.csv(kaggel,file="trees.csv")
```












